---
title: "Extending the Findings of Walker et Al."
author: "Elena Voulgaris and Abby Suber"
format: 
  beamer:
    aspectratio: 169
    theme: Madrid 
editor: visual
excecute: 
  echo: false
  warning: false
  message: false
---

```{r}
#| include: false

source(here::here("importdata.R"))
source(here::here("retentiondata.R"))
source(here::here("combineddata.R"))
source(here::here("figures.R"))
```

## Introduction

\[why did we do this\]

## Data

To perform this replication, it was necessary to add additional data to our analysis:

- IPEDS admissions (ADM), institution directory (HD), and fall enrollment (EF-C) surveys from the years 2023 & 2024.

- Additional fall enrollment survey EF-D from each year analyzed; this survey contains the annual retention rate.

## Data: Roadmap

\[how did we do this, steps, etc\]

## Results: Figure 1, Extended

```{r}
figure_1
```

## Results: Figure a1, Extended

```{r}
figure_a1
```

## Results: Figure a2, Extended

```{r}
figure_a2
```

## Results: Figure a3, Extended

```{r}
figure_a3
```

## Results: Figure a4, Extended

```{r}
figure_a4
```

## Results: Retention Analysis

```{r}
figure_retention
```

## Conclusion

\[what did we learn\]
